Price of Anarchy for Mean Field Games

### 2018-07-26 PoA.tex
simplify prop 4 & prop 6

% proposition b_2 to \infty
\begin{proposition}
	Assuming (\ref{eq:assumptions}), and the initial condition $\xi$ satisfies $\mathbb{E}(\xi)\neq 0$, $q_T+\bar{q}_T(1-s_T)>0$ and $q_T+\bar{q}_T(1-s_T)^2>0$.
	If 
	\begin{equation*}
	\frac{q+\bar{q}(1-s)}{r+\bar{r}(1-\bar{s})} =\frac{q+\bar{q}(1-s)^2}{r+\bar{r}(1-\bar{s})^2}
	\end{equation*}
	then 
	$$ \lim_{b_2 \to \infty} PoA = 1,$$	
	otherwise, 
	$$ \lim_{b_2 \to \infty} PoA >1$$.
\label{prop:b2_to_infty}
\end{proposition}

@@

\begin{proof}
	When $b_2 \to \infty$, we have:
	\begin{equation*}
	\begin{array}{l}
	\lambda^{b_2} \to \frac{r + \bar{r}(1-\bar{s})^2}{r + \bar{r}(1-\bar{s})} =: \lambda^{b_2 \to \infty}, \\
	B^{b_2} \to \infty, \qquad B^{\eta,b_2} \to \infty\\
	C^{u,b_2} \to \lambda^{b_2 \to \infty} ( q + \bar{q}(1-s)) =: C^{u,b_2 \to \infty}, \qquad D^{u,b_2} \to \lambda^{b_2 \to \infty} (q_T + \bar{q}_T(1-s_T)) =: D^{u,b_2 \to \infty} >0,
	\end{array}
	\end{equation*}
	and $A^{u}, (A^{w}, C^w, D^w), (A^{\eta}, C^{\eta}, D^{\eta})$ are independent of  $b_2$. Moreover, we notice that:
	\begin{equation*}
		\frac{\delta_u^{\pm,b_2}}{b_2 + \bar{b}_2} = -\frac{A^u}{b_2 + \bar{b}_2} \pm \sqrt{\frac{(A^u)^2}{(b_2+\bar{b}_2)^2}+\frac{C^{u,b_2}}{r + \bar{r}(1-\bar{s})^2} } \xrightarrow[b_2 \to \infty]{} \displaystyle \pm \sqrt{\frac{q + \bar{q}(1-s)}{r + \bar{r}(1-\bar{s})} } =: \pm c_{\delta_u^{b_2 \to \infty}}.
	\end{equation*}
	and thus, $\delta^{+,b_2}_u - \delta^{-,b_2}_u \xrightarrow[b_2 \to \infty]{} +\infty$.
	From the assumption $q_T+\bar{q}_T(1-s_T)>0$, we have $D^u>0$. From equation (\ref{eq:riccati_ut_sol}), for each $t \in[0,T)$, we deduce:
	\begin{IEEEeqnarray*}{rCl}
		(b_2 + \bar{b}_2) u^{b_2}_t &=& \frac{ \displaystyle  \left(\frac{C^{u,b_2}}{b_2 + \bar{b}_2} + D^{u,b_2} \cdot \frac{\delta^{+,b_2}_u}{b_2 + \bar{b}_2}\right) - \left(\frac{C^{u,b_2}}{b_2 + \bar{b}_2} + D^{u,b_2} \cdot \frac{\delta^{-,b_2}_u}{b_2 + \bar{b}_2}\right)e^{- (\delta^{+,b_2}_u - \delta^{-,b_2}_u)(T-t)} }
		{\displaystyle \left(\frac{- \delta^{-,b_2}_u}{(b_2 + \bar{b}_2)^2} + \frac{D^{u,b_2}}{r + \bar{r}(1-\bar{s})^2} \right) + \left(\frac{\delta^{+,b_2}_u}{(b_2 + \bar{b}_2)^2} - \frac{D^{u,b_2} }{r + \bar{r}(1-\bar{s})^2} \right)e^{- (\delta^{+,b_2}_u - \delta^{-,b_2}_u)(T-t)}  } \nonumber \\
		&&\\
		&\xrightarrow[b_2 \to \infty]{}& \quad (r + \bar{r}(1-\bar{s})^2) \cdot c_{\delta_u^{b_2 \to \infty}}  =: c_u
	\end{IEEEeqnarray*}
	Idem, for any $t \in [0,T)$,
	$$ (b_2 + \bar{b}_2) w_t^{b_2} \xrightarrow[b_2 \to \infty]{}  (r + \bar{r}(1-\bar{s})^2) \cdot c_{\delta_w^{b_2 \to \infty}} =: c_w,\qquad \text{with } \quad c_{\delta_w^{b_2 \to \infty}} = \sqrt{ \frac{q + \bar{q}(1-s)^2}{r + \bar{r}(1-\bar{s})^2} }.$$

	% lower bound for (b_2 + b2 bar) u_t
	Next, we derive a strictly positive uniform lower bound for $(b_2 + \bar{b}_2) u_t^{b_2}$ over $[0,T]$ and large $b_2$. Let $\zeta_1 =\frac{1}{2} \min \left\{ c_{\delta_u^{b_2 \to \infty}}, D^{u,b_2 \to \infty} \right\}$. Then there exists $b_2^{*,lower}>0$ such that for all $b_2 \geq b_2^{*,lower}$,
	$$ 
	\max \left\{  \left\vert \frac{\delta_u^{+,b_2}}{b_2 + \bar{b}_2}  - c_{\delta_u^{b_2 \to \infty}} \right\vert, \   \left\vert \frac{\delta_u^{-,b_2}}{b_2 + \bar{b}_2}  - \left(-c_{\delta_u^{b_2 \to \infty}}\right) \right\vert, \vert D^{u,b_2} - D^{u,b_2\to \infty} \vert,  \left\vert \frac{1}{b_2 + \bar{b}_2} \right\vert  \right\} \leq \zeta_1,
	$$ 
	and thus for all $t \in [0,T]$,
	\begin{IEEEeqnarray}{rCl}
		(b_2 + \bar{b}_2) u_t^{b_2} &\geq&  (b_2 + \bar{b}_2) \frac{D^{u,b_2} \delta_u^{+, b_2} }{ (\delta_u^{+,b_2} - \delta_u^{-,b_2}) + B^{b_2}D^{u,b_2} } \nonumber \\
		&=& \frac{D^{u,b_2} \frac{\delta_u^{+, b_2}}{b_2+ \bar{b}_2} }{ \frac{1}{b_2 + \bar{b}_2} \cdot \frac{\delta_u^{+,b_2} - \delta_u^{-,b_2}}{b_2 + \bar{b}_2} + \frac{D^{u,b_2}}{r + \bar{r}(1-\bar{s})^2} } \nonumber \\
		&\geq& \frac{(D^{u,b_2 \to \infty} - \zeta_1 ) \cdot (c_{\delta_u^{b_2 \to \infty}} - \zeta_1) }{ \zeta_1 \cdot (2 c_{\delta_u^{b_2 \to \infty}} + 2 \zeta_1) + (D^{u,b_2 \to \infty} + \zeta_1) / (r+ \bar{r}(1-\bar{s})^2) } =: m_u>0.
	\label{eq:ut_uniform_lower_bound_b2_infinity}
	\end{IEEEeqnarray}
	Idem, we can have a strictly positive uniform lower bound for $b_2 \eta_t^{b_2}$ over $[0,T]$ and large $b_2$. Let $b^{*,\eta,lower}_2 >0$ such that for all $b_2 \geq b^{*,\eta,lower}$,
	\begin{equation}
		b_2 \eta_t^{b_2} \geq m_\eta > 0.
	\label{eq:eta_t_uniform_lower_bound_b2_infinity}
	\end{equation}

	% upper bound for u_t, w_t
	Also, from equation (\ref{eq:riccati_ut_sol}), for any fixed $b_2$, we can compute the derivative of $u_t^{b_2}$ with respect to time $t$:
	\begin{equation*}
		\frac{d u_t^{b_2}}{dt} = \frac{\left(B^{b_2} (D^{u,b_2})^2 + 2 A^u D^{u,b_2} - C^{u,b_2} \right) \cdot \left(\delta_u^{+,b_2} - \delta_u^{-,b_2}\right)^2 e^{- (\delta_u^{+,b_2} - \delta_u^{-,b_2})(T-t) } }{\left[B^{b_2} D^{u,b_2}(1-e^{- (\delta_u^{+,b_2} - \delta_u^{-,b_2})(T-t)})   + \delta_u^{+,b_2}e^{- (\delta_u^{+,b_2} - \delta_u^{-,b_2})(T-t)}- \delta_u^{-,b_2}  \right]^2 }.
	\end{equation*}
	Hence, the function $t \mapsto u_t^{b_2}$ is increasing if $B^{b_2} (D^{u,b_2})^2 + 2 A^u D^{u,b_2} - C^{u,b_2} > 0$. Since 
	$$\lim_{b_2 \to \infty} B^{b_2} (D^{u,b_2})^2 + 2 A^u D^{u,b_2} - C^{u,b_2} = \infty,$$
	there exists $b_2^{*,u,upper}>b_2^{*,lower}$ such that for all $b_2 \geq b_2^{*,u,upper}$, we have $t \mapsto u_t^{b_2}$ is increasing and 
	$$ \sup_{b_2 \geq b_2^{*,u,upper}} \sup_{0\leq t \leq T} \left\{ u_t^{b_2} \right\} = \sup_{b_2 \geq b_2^{*,u,upper}} \left\{ u_T^{b_2}\right\}  = \sup_{b_2 \geq b_2^{*,u,upper}} \{ D^{u,b_2}  \} \leq D^{u,b_2 \to \infty} + \zeta_1.$$
	Thus,
	\begin{equation}
	\left| u_t^{b_2}\right|\leq D^{u,b_2 \to \infty} + \zeta_1 ,\ t\in[0,T],\ b_2 > b_2^{*,u,upper},
	\label{eq:u_t_bound}
	\end{equation}
	and by the same argument,
	\begin{equation}	
	\left| w_t^{b_2}\right|\leq D^{w} ,\ t\in[0,T],\ b_2 > b_2^{*,w,upper}.
	\label{eq:w_t_bound}
	\end{equation}
	Let $b_2^{*,upper} = \max \{ b_2^{*,u,upper}, b_2^{*,w,upper}\}$ and $M = \max \{  D^{u,b_2 \to \infty}+\zeta_1, D^w\}$.\\

	In the case when
	\begin{equation*}
	\frac{q+\bar{q}(1-s)}{r+\bar{r}(1-\bar{s})}=\frac{q+\bar{q}(1-s)^2}{r+\bar{r}(1-\bar{s})^2},
	\end{equation*}
	we have $c_{\delta_u^{b_2 \to \infty}}=c_{\delta_w^{b_2 \to \infty}}$ and so that $c_u = c_w =: c$. 
	We would like to show that $\lim_{b_2 \to \infty} \frac{\Delta SC}{SC^{MKV}} = 0$. Our approach is to split the interval $[0,T]$ into two parts: $[0,\frac{T}{2}]$ and $[\frac{T}{2},T]$.	
	Since $v^{b_2}_t \geq 0$ for all $t\in [0,T]$, we have $SC^{MKV,b_2} \geq w_0^{b_2} (\mathbb{E}(\xi))^2$.	For the sake of simplicity, we denote $h_u(b_2,t) := (b_2 + \bar{b}_2) u_{t}^{b_2}$ and $h_w(b_2,t) := (b_2 + \bar{b}_2)w_t^{b_2}$. We have:
	\begin{equation}
	\begin{split}
		\frac{\Delta SC^{b_2}}{SC^{MKV,b_2}} &\leq \frac{1}{w_0^{b_2} \mathbb{E}(\xi)^2 } \left( B^{b_2} \int_{0}^{\frac{T}{2}} (u_t^{b_2} - w_t^{b_2})^2 (\bar{x}_t^{MFG,b_2})^2 dt + B^{b_2} \int_{\frac{T}{2}}^{T} (u_t^{b_2} - w_t^{b_2})^2 (\bar{x}_t^{MFG,b_2})^2 dt \right) \\ 
		&=  \frac{1}{(b_2 + \bar{b}_2) w_0^{b_2} } \left( I_1^{b_2} + I_2^{b_2} \right),
	\end{split}
	\label{eq:I_1_plus_I_2}
	\end{equation}
	where:
	\begin{IEEEeqnarray*}{rCl}
	I_1^{b_2} &=& \frac{(b_2 + \bar{b}_2)^3}{r + \bar{r}(1-\bar{s})^2}  \int_0^{\frac{T}{2}} (u_t^{b_2} - w_t^{b_2})^2 e^{2(b_1 + \bar{b}_1)t} \exp \left( -2B^{b_2} \int_0^{t} u_s^{b_2} ds 
	\right) dt \\
	&=& \frac{b_2 + \bar{b}_2}{r + \bar{r}(1-\bar{s})^2} \int_0^{\frac{T}{2}} [ h_u(b_2,t)- h_w(b_2,t) ]^2 \cdot e^{2(b_1 + \bar{b}_1)t} \exp \left( - \frac{2 (b_2 + \bar{b}_2)}{r+ \bar{r}(1-\bar{s})^2}  \int_0^t h_u(b_2,s) ds \right) dt, 
	\end{IEEEeqnarray*}
	and:
	$$
		I_2^{b_2} = \frac{(b_2 + \bar{b}_2)^3}{r + \bar{r}(1-\bar{s})^2}  \int_{\frac{T}{2}}^T (u_t^{b_2} - w_t^{b_2})^2 e^{2(b_1 + \bar{b}_1)t} \exp \left( -\frac{2 (b_2 + \bar{b}_2)}{r + \bar{r}(1-\bar{s})^2} \int_0^{t} h_u(b_2,s) ds \right) dt.
	$$

	Fix $\epsilon>0$. In the following, we show that $I_1^{b_2} \leq \epsilon$ and $I_2^{b_2} \leq \epsilon$ for large $b_2$.
	% the term I_1
	First, consider $I_1^{b_2}$. Recall that for $t \in[0,T/2]$, we have $\lim_{b_2 \to \infty}h_u(b_2,t) = \lim_{b_2 \to \infty}h_w(b_2,t) = c$, and for all $b_2 \geq b_2^{*,upper}$, the functions $[0,T/2] \ni s \mapsto u_s^{b_2}$ and $[0,T/2] \ni s \mapsto w_s^{b_2}$ are increasing, and thus, $[0,T/2] \ni s \mapsto h_u(b_2,t)$ and $[0,T/2] \ni s \mapsto h_w(b_2,t)$ are increasing. (Note that $T/2<T$ is chosen arbitrarily, since the above limits do not hold at $T$.) Let 
	$$ \zeta_2 =\min \{\frac{1}{2}\sqrt{\epsilon c}e^{-T(b_1+\bar{b}_2)},\frac{c}{2}\}.$$
	Then there exists $b_2^{*,I_1}  > b_2^{*,upper}$ such that for all $b_2 \geq b_2^{*,I_1}$ and all $s\in [0, T/2]$ we have:
	\begin{equation*}
	\begin{array}{lclclclcl}
		c - \zeta_2 &\leq& h_u(b_2,0) &\leq& h_u(b_2,s) &\leq& h_u(b_2, T/2 ) &\leq& c + \zeta_2, \\
		c - \zeta_2 &\leq& h_w(b_2,0) &\leq& h_w(b_2,s) &\leq& h_w(b_2, T/2 ) &\leq& c + \zeta_2.
	\end{array}
	\end{equation*}
	Thus, for any $t \in [0,\frac{T}{2}]$ and $b_2 \geq b_2^{*,I_1}$, we have:
	$$
		\vert h_u(b_2, t) - h_w(b_2,t) \vert^2 \leq  4 \zeta_2^2 \quad \text{and} \quad \int_0^t h_u(b_2,s)ds \geq (c - \zeta_2) t \geq \frac{c}{2}\cdot t.
	$$
	Therefore,
	\begin{IEEEeqnarray}{rCl}
		I_1^{b_2} &\leq& 4\zeta_2^2e^{2T(b_1 + \bar{b}_1)} \cdot\frac{(b_2 + \bar{b}_2)}{r+ \bar{r}(1-\bar{s})^2} \int_0^{\frac{T}{2}} \exp \left(  - \frac{2 (b_2 + \bar{b}_2)}{r + \bar{r}(1-\bar{s})^2} \cdot \frac{c}{2}\cdot t \right) dt \nonumber \\
		&=& \frac{4e^{2T(b_1 + \bar{b}_1)}}{c}\cdot  \left( 1 - e^{ - \frac{(b_2 + \bar{b}_2) c}{r + \bar{r}(1-\bar{s})^2}  \frac{T}{2} } \right) \cdot \zeta_2^2 \leq \epsilon, 
	\label{eq:I1_ineq_b2_infinity}
	\end{IEEEeqnarray}
	where the last inequality comes from the definition of $\zeta_2$.

>>>>

% proposition b_2 to \infty
\begin{proposition}
	Assuming (\ref{eq:assumptions}), and the initial condition $\xi$ satisfies $\mathbb{E}(\xi)\neq 0$. Moreover, we assume that $q_T+\bar{q}_T(1-s_T)>0$, $q_T+\bar{q}_T(1-s_T)^2>0$ and $q_T + \bar{q}_T > 0$.

	If 
	\begin{equation*}
	\frac{q+\bar{q}(1-s)}{r+\bar{r}(1-\bar{s})} =\frac{q+\bar{q}(1-s)^2}{r+\bar{r}(1-\bar{s})^2}
	\end{equation*}
	then 
	$$ \lim_{b_2 \to \infty} PoA = 1,$$	
	otherwise, 
	$$ \lim_{b_2 \to \infty} PoA >1.$$
\label{prop:b2_to_infty}
\end{proposition}

@@

\begin{proof}
	When $b_2 \to \infty$, we have:
	\begin{equation*}
	\begin{array}{l}
	\lambda^{b_2} \to \frac{r + \bar{r}(1-\bar{s})^2}{r + \bar{r}(1-\bar{s})} =: \lambda^{b_2 \to \infty}, \\
	B^{b_2} \to \infty, \qquad B^{\eta,b_2} \to \infty\\
	C^{u,b_2} \to \lambda^{b_2 \to \infty} ( q + \bar{q}(1-s)) =: C^{u,b_2 \to \infty}, \qquad D^{u,b_2} \to \lambda^{b_2 \to \infty} (q_T + \bar{q}_T(1-s_T)) =: D^{u,b_2 \to \infty} >0,
	\end{array}
	\end{equation*}
	and $A^{u}, (A^{w}, C^w, D^w), (A^{\eta}, C^{\eta}, D^{\eta})$ are independent of  $b_2$. Moreover, we notice that:
	\begin{equation*}
		\frac{\delta_u^{\pm,b_2}}{b_2 + \bar{b}_2} = -\frac{A^u}{b_2 + \bar{b}_2} \pm \sqrt{\frac{(A^u)^2}{(b_2+\bar{b}_2)^2}+\frac{C^{u,b_2}}{r + \bar{r}(1-\bar{s})^2} } \xrightarrow[b_2 \to \infty]{} \displaystyle \pm \sqrt{\frac{q + \bar{q}(1-s)}{r + \bar{r}(1-\bar{s})} } =: \pm c_{\delta_u^{b_2 \to \infty}}.
	\end{equation*}
	and thus, $\delta^{+,b_2}_u - \delta^{-,b_2}_u \xrightarrow[b_2 \to \infty]{} +\infty$.
	From the assumption $q_T+\bar{q}_T(1-s_T)>0$, we have $D^u>0$. From equation (\ref{eq:riccati_ut_sol}), for each $t \in[0,T)$, we deduce:
	\begin{IEEEeqnarray*}{rCl}
		(b_2 + \bar{b}_2) u^{b_2}_t &=& \frac{ \displaystyle  \left(\frac{C^{u,b_2}}{b_2 + \bar{b}_2} + D^{u,b_2} \cdot \frac{\delta^{+,b_2}_u}{b_2 + \bar{b}_2}\right) - \left(\frac{C^{u,b_2}}{b_2 + \bar{b}_2} + D^{u,b_2} \cdot \frac{\delta^{-,b_2}_u}{b_2 + \bar{b}_2}\right)e^{- (\delta^{+,b_2}_u - \delta^{-,b_2}_u)(T-t)} }
		{\displaystyle \left(\frac{- \delta^{-,b_2}_u}{(b_2 + \bar{b}_2)^2} + \frac{D^{u,b_2}}{r + \bar{r}(1-\bar{s})^2} \right) + \left(\frac{\delta^{+,b_2}_u}{(b_2 + \bar{b}_2)^2} - \frac{D^{u,b_2} }{r + \bar{r}(1-\bar{s})^2} \right)e^{- (\delta^{+,b_2}_u - \delta^{-,b_2}_u)(T-t)}  } \nonumber \\
		&&\\
		&\xrightarrow[b_2 \to \infty]{}& \quad (r + \bar{r}(1-\bar{s})^2) \cdot c_{\delta_u^{b_2 \to \infty}}  =: c_u
	\end{IEEEeqnarray*}
	Idem, for all $t \in [0,T)$,
	$$ (b_2 + \bar{b}_2) w_t^{b_2} \xrightarrow[b_2 \to \infty]{}  (r + \bar{r}(1-\bar{s})^2) \cdot c_{\delta_w^{b_2 \to \infty}} =: c_w,\qquad \text{with } \quad c_{\delta_w^{b_2 \to \infty}} = \sqrt{ \frac{q + \bar{q}(1-s)^2}{r + \bar{r}(1-\bar{s})^2} },$$
	and
	$$ b_2 \eta_t^{b_2} \xrightarrow[b_2 \to \infty]{} (r + \bar{r}) \cdot c_{\delta_{\eta}^{b_2 \to \infty}} =: c_\eta, \qquad \text{with } \quad c_{\delta_\eta^{b_2 \to \infty}} = \sqrt{ \frac{q + \bar{q}}{r +\bar{r}} }.$$

	% lower bound for (b_2 + b2 bar) u_t
	Next, we derive a strictly positive uniform lower bound for $(b_2 + \bar{b}_2) u_t^{b_2}$ over $[0,T]$ and large $b_2$. Let $\zeta_1 =\frac{1}{2} \min \left\{ c_{\delta_u^{b_2 \to \infty}}, D^{u,b_2 \to \infty} \right\}$. Then there exists $b_2^{*,u,lower}>0$ such that for all $b_2 \geq b_2^{*,u,lower}$,
	$$ 
	\max \left\{  \left\vert \frac{\delta_u^{+,b_2}}{b_2 + \bar{b}_2}  - c_{\delta_u^{b_2 \to \infty}} \right\vert, \   \left\vert \frac{\delta_u^{-,b_2}}{b_2 + \bar{b}_2}  - \left(-c_{\delta_u^{b_2 \to \infty}}\right) \right\vert, \vert D^{u,b_2} - D^{u,b_2\to \infty} \vert,  \left\vert \frac{1}{b_2 + \bar{b}_2} \right\vert  \right\} \leq \zeta_1,
	$$ 
	and thus for all $t \in [0,T]$,
	\begin{IEEEeqnarray}{rCl}
		(b_2 + \bar{b}_2) u_t^{b_2} &\geq&  (b_2 + \bar{b}_2) \frac{D^{u,b_2} \delta_u^{+, b_2} }{ (\delta_u^{+,b_2} - \delta_u^{-,b_2}) + B^{b_2}D^{u,b_2} } \nonumber \\
		&\geq& \frac{(D^{u,b_2 \to \infty} - \zeta_1 ) \cdot (c_{\delta_u^{b_2 \to \infty}} - \zeta_1) }{ \zeta_1 \cdot (2 c_{\delta_u^{b_2 \to \infty}} + 2 \zeta_1) + (D^{u,b_2 \to \infty} + \zeta_1) / (r+ \bar{r}(1-\bar{s})^2) } =: m_u>0.
	\label{eq:ut_uniform_lower_bound_b2_infinity}
	\end{IEEEeqnarray}
	Then, by the same technique in inequality (\ref{eq:ut_uniform_lower_bound_b2_infinity}), there exists $b_2^{*,\eta, lower} > 0$ and $m_\eta >0$ such that for all $b_2 \geq b_2^{*,\eta,lower}$,
	\begin{equation}
	   b_2 \eta_t^{b_2} \geq m_\eta.
	\label{eq:eta_t_uniform_lower_bound_b2_infinity}
	\end{equation}

	% upper bound for u_t, w_t
	Also, from equation (\ref{eq:riccati_ut_sol}), for any fixed $b_2$, we can compute the derivative of $u_t^{b_2}$ with respect to time $t$:
	\begin{equation*}
		\frac{d u_t^{b_2}}{dt} = \frac{\left(B^{b_2} (D^{u,b_2})^2 + 2 A^u D^{u,b_2} - C^{u,b_2} \right) \cdot \left(\delta_u^{+,b_2} - \delta_u^{-,b_2}\right)^2 e^{- (\delta_u^{+,b_2} - \delta_u^{-,b_2})(T-t) } }{\left[B^{b_2} D^{u,b_2}(1-e^{- (\delta_u^{+,b_2} - \delta_u^{-,b_2})(T-t)})   + \delta_u^{+,b_2}e^{- (\delta_u^{+,b_2} - \delta_u^{-,b_2})(T-t)}- \delta_u^{-,b_2}  \right]^2 }.
	\end{equation*}
	Hence, the function $t \mapsto u_t^{b_2}$ is increasing if $B^{b_2} (D^{u,b_2})^2 + 2 A^u D^{u,b_2} - C^{u,b_2} > 0$. Since 
	$$\lim_{b_2 \to \infty} B^{b_2} (D^{u,b_2})^2 + 2 A^u D^{u,b_2} - C^{u,b_2} = \infty,$$
	there exists $b_2^{*,u,upper} >0$ such that for all $b_2 \geq b_2^{*,u,upper}$, we have $t \mapsto u_t^{b_2}$ is increasing and 
	$$ \sup_{b_2 \geq b_2^{*,u,upper}} \sup_{0\leq t \leq T} \left\{ u_t^{b_2} \right\} = \sup_{b_2 \geq b_2^{*,u,upper}} \left\{ u_T^{b_2}\right\}  = \sup_{b_2 \geq b_2^{*,u,upper}} \{ D^{u,b_2}  \} \leq D^{u,b_2 \to \infty} + 1.$$
	Thus,
	\begin{equation*}
	\left\vert u_t^{b_2}\right\vert \leq D^{u,b_2 \to \infty} + 1 , \quad \forall \  t\in[0,T],\ b_2 \geq b_2^{*,u,upper},
	\label{eq:u_t_bound}
	\end{equation*}
	and by the same argument for $w_t^{b_2}$ and $\eta_t^{b_2}$, there exists $b_2^{*,upper} \geq b_2^{*,u,upper}$ such that
	%for all $t \in [0,T]$ and $b_2 \geq b_2^{*,w,upper}$,
	%\begin{equation*}	
	%$\left| w_t^{b_2}\right|\leq D^{w}.$
	%\label{eq:w_t_bound}
	%\end{equation*}

	%Let $b_2^{*,upper} = \max \{ b_2^{*,u,upper}, b_2^{*,w,upper}\}$ and $M = \max \{  D^{u,b_2 \to \infty}+\zeta_1, D^w\}$, then\\
	\begin{equation}
	\sup_{b_2 \geq b_2^{*,upper}} \sup_{0 \leq t \leq T} \max \left\{ \vert u_t^{b_2} \vert , \vert w_t^{b_2} \vert, \vert \eta_t^{b_2} \vert \right\} \leq M.
	\label{eq:ut_wt_upper_bound_b2_infty}
	\end{equation}
	and the functions $t \mapsto u_t^{b_2}$, $t \mapsto w_t^{b_2}$ and $t \mapsto \eta_t^{b_2}$ are increasing along $[0,T]$. \\

	\textbf{Case 1:} when
	\begin{equation*}
	\frac{q+\bar{q}(1-s)}{r+\bar{r}(1-\bar{s})}=\frac{q+\bar{q}(1-s)^2}{r+\bar{r}(1-\bar{s})^2},
	\end{equation*}
	we have $c_{\delta_u^{b_2 \to \infty}}=c_{\delta_w^{b_2 \to \infty}}$ and so that $c_u = c_w =: c$. 
	We would like to show that $\lim_{b_2 \to \infty} \frac{\Delta SC}{SC^{MKV}} = 0$. Our approach is to split the interval $[0,T]$ into two parts: $[0,T/2]$ and $[T/2,T]$.	
	Since $v^{b_2}_t \geq 0$ for all $t\in [0,T]$, we have $SC^{MKV,b_2} \geq w_0^{b_2} (\mathbb{E}(\xi))^2$.	For the sake of simplicity, we denote $h_u(b_2,t) := (b_2 + \bar{b}_2) u_{t}^{b_2}$ and $h_w(b_2,t) := (b_2 + \bar{b}_2)w_t^{b_2}$. We have:
	\begin{equation}
	\begin{split}
		\frac{\Delta SC^{b_2}}{SC^{MKV,b_2}} &\leq \frac{1}{w_0^{b_2} \mathbb{E}(\xi)^2 } \left( B^{b_2} \int_{0}^{\frac{T}{2}} (u_t^{b_2} - w_t^{b_2})^2 (\bar{x}_t^{MFG,b_2})^2 dt + B^{b_2} \int_{\frac{T}{2}}^{T} (u_t^{b_2} - w_t^{b_2})^2 (\bar{x}_t^{MFG,b_2})^2 dt \right) \\ 
		&=  \frac{1}{(b_2 + \bar{b}_2) w_0^{b_2} } \left( I_1^{b_2} + I_2^{b_2} \right),
	\end{split}
	\label{eq:I_1_plus_I_2}
	\end{equation}
	where:
	\begin{IEEEeqnarray*}{rCl}
	I_1^{b_2} &=& \frac{(b_2 + \bar{b}_2)^3}{r + \bar{r}(1-\bar{s})^2}  \int_0^{\frac{T}{2}} (u_t^{b_2} - w_t^{b_2})^2 e^{2(b_1 + \bar{b}_1)t} \exp \left( -2B^{b_2} \int_0^{t} u_s^{b_2} ds 
	\right) dt \\
	&=& \frac{b_2 + \bar{b}_2}{r + \bar{r}(1-\bar{s})^2} \int_0^{\frac{T}{2}} [ h_u(b_2,t)- h_w(b_2,t) ]^2 \cdot e^{2(b_1 + \bar{b}_1)t} \exp \left( - \frac{2 (b_2 + \bar{b}_2)}{r+ \bar{r}(1-\bar{s})^2}  \int_0^t h_u(b_2,s) ds \right) dt, 
	\end{IEEEeqnarray*}
	and:
	$$
		I_2^{b_2} = \frac{(b_2 + \bar{b}_2)^3}{r + \bar{r}(1-\bar{s})^2}  \int_{\frac{T}{2}}^T (u_t^{b_2} - w_t^{b_2})^2 e^{2(b_1 + \bar{b}_1)t} \exp \left( -\frac{2 (b_2 + \bar{b}_2)}{r + \bar{r}(1-\bar{s})^2} \int_0^{t} h_u(b_2,s) ds \right) dt.
	$$

	Fix $\epsilon>0$. In the following, we show that $I_1^{b_2} \leq \epsilon$ and $I_2^{b_2} \leq \epsilon$ for large $b_2$.
	% the term I_1
	First, consider $I_1^{b_2}$. Recall that for $t \in[0,T/2]$, we have $\lim_{b_2 \to \infty}h_u(b_2,t) = \lim_{b_2 \to \infty}h_w(b_2,t) = c$, and for all $b_2 \geq b_2^{*,upper}$, the functions $[0,T/2] \ni s \mapsto u_s^{b_2}$ and $[0,T/2] \ni s \mapsto w_s^{b_2}$ are increasing, and thus, $[0,T/2] \ni s \mapsto h_u(b_2,t)$ and $[0,T/2] \ni s \mapsto h_w(b_2,t)$ are increasing. (Note that $T/2<T$ is chosen arbitrarily, since the above limits do not hold at $T$.) Let 
	$$ \zeta_2 = \min \left\{ \frac{c}{2},  \frac{1}{2} e^{-T(b_1+\bar{b}_2)} \sqrt{\epsilon c} \right\}.$$
	Then there exists $b_2^{*,I_1}  > b_2^{*,upper}$ such that for all $b_2 \geq b_2^{*,I_1}$ and all $s\in [0, T/2]$ we have:
	\begin{equation*}
	\begin{array}{lclclclcl}
		c - \zeta_2 &\leq& h_u(b_2,0) &\leq& h_u(b_2,s) &\leq& h_u(b_2, T/2 ) &\leq& c + \zeta_2, \\
		c - \zeta_2 &\leq& h_w(b_2,0) &\leq& h_w(b_2,s) &\leq& h_w(b_2, T/2 ) &\leq& c + \zeta_2.
	\end{array}
	\end{equation*}
	Thus, for any $t \in [0,\frac{T}{2}]$ and $b_2 \geq b_2^{*,I_1}$, we have:
	$$
		\vert h_u(b_2, t) - h_w(b_2,t) \vert^2 \leq  4 \zeta_2^2 \quad \text{and} \quad \int_0^t h_u(b_2,s)ds \geq (c - \zeta_2) t \geq \frac{c}{2}\cdot t.
	$$
	Therefore,
	\begin{IEEEeqnarray}{rCl}
		I_1^{b_2} &\leq& 4\zeta_2^2e^{2T(b_1 + \bar{b}_1)} \cdot\frac{(b_2 + \bar{b}_2)}{r+ \bar{r}(1-\bar{s})^2} \int_0^{\frac{T}{2}} \exp \left(  - \frac{2 (b_2 + \bar{b}_2)}{r + \bar{r}(1-\bar{s})^2} \cdot \frac{c}{2}\cdot t \right) dt \nonumber \\
		&=& \frac{4e^{2T(b_1 + \bar{b}_1)}}{c}\cdot  \left( 1 - e^{ - \frac{(b_2 + \bar{b}_2) c}{r + \bar{r}(1-\bar{s})^2}  \frac{T}{2} } \right) \cdot \zeta_2^2 \leq \epsilon, 
	\label{eq:I1_ineq_b2_infinity}
	\end{IEEEeqnarray}
	where the last inequality comes from the definition of $\zeta_2$.
